Baseline centering problem

### 2018-12-13 paper/tangotd.tex

When sampling for the right Bellman equation, it is wasteful to sample a
state $s_2$ and apply a test function $\psi$ if $\psi(s_2)$ is very
small. Instead one may want to sample $s_2$ according to
$\rho_\psi\deq \rho(s_2)\abs{\psi(s_2)}/\E_{\rho}\abs{\psi}$, in which case
$\E_{s_2\sim \rho} f(s_2)\psi(s_2)$ becomes $\E_{s_2\sim \rho_\psi}
f(s_2)(\E_{\rho}\abs{\psi})$. This may significantly reduce variance.

>>>>

When sampling for the right Bellman equation, it is wasteful to sample a
state $s_2$ and apply a test function $\psi$ if $\psi(s_2)$ is very
small. Instead one may want to sample $s_2$ according to
$\rho_\psi\deq \rho(s_2)\abs{\psi(s_2)}/\E_{\rho}\abs{\psi}$, in which case
$\E_{s_2\sim \rho} f(s_2)\psi(s_2)$ is equal to $\E_{s_2\sim \rho_\psi}
f(s_2)(\E_{\rho}\abs{\psi})$. This will significantly reduce variance,
especially for test functions $\psi$ that are concentrated aroudn a few
points.
